### 2019-08-31 depr_presentation/main.tex
Code: Change plot marker

% % % % % % % % % % % % % % % % % % % % % % % % % %

\blank [big, force]
\Title {Dantzig Selector \\ Applied on mm-Wave MIMO: \\ Part I. Expected Error Analysis}
\blank [big]
\Subtitle {Presenter: Tzu-Yu Jeng \\ Advisor: Prof.\ H.J.\ Su}
\blank [big]
\Subsubtitle{May 30, 2019}
\Subsubtitle{Graduate Instute of Commnication Engineering, \\ National Taiwan University}

\page[yes] % % % % % % % % % % % % % % % % % % % % % % % % % %

\Frametitle {Organization}

\startitemize
\I Problem Configuration Proposed Method
\I Sparsity of Angular Channel Matrix
\I Concentration Inequality of \m {\M{P}}
\I Restricted Isometry of \m {\M{P}}
\I Expected Error of Dantzig Selector
\I Conclusion and Future Work
\I References
\stopitemize

@@

\Frametitle {Background}
\startitemize

\I Multiple-input-multiple-output (MIMO) wireless communication is widely expected to be the next-generation communication scheme
\I But reliable communication requires that the channel response be known at the receiver to facilitate, say, beamforming algorithm and channel calibration
\I And in the MIMO system, estimating wireless channels calls for high complexity
\I Meanwhile, in the millimeter wave r\`egime, which is often used together with MIMO, channel often exhibits sparse properties
\I If the sparsity is exploited, can few observations suffice to estimate the channel?

\stopitemize

\Frametitle {Compressive Sensing}
\startitemize

\I Recent developement on channel estimation is facilitated by advances of so-called compressed sensing (CS)
\I CS addresses the common situation in statsitical applications that the number of model parameters \m {} the number of measurements \m {}.
\I With insufficient (possibly noisy) measurements, how well can we recover all \m {} parameters?
Of course, more assumption must be made.
\I Work on CS reveals that few observations of the signal may be sufficient for us to resonstruct the signal when it is sparse.
\I In the advent, Cand\`es and Tao (2006) proposes the Dantzig Selector (DS).
It was first applied in channel estimation context

\stopitemize

\Frametitle {Notation}
\startitemize

\I \m {} denotes vectors
\I \m {} denotes matrices
\I \m {} refers to either \m {} or \m {}.
\I \m {} is the Hilbert space \m {} over \m {}
\I \m {} is the collection of \m {} by \m {} matrices.
\I \m {} denotes the \m {}-norm of \m {}

\stopitemize

\Frametitle {Definitions: Sparsity}
\startitemize

\I Suppose \m {}.
Let \m {}.
Denote as \m {} the columns of \m {} having indices in \m {}.
\I \m {} is called \m {}-sparse with support \m {}, \m {}, if only at most \m {} components of \m {} is nonzero.
\I (New def.) We say \m {} is almost-\m {}-sparse with \m {}-residue \m {}, if \m {} where \m {} is sorted in magnitude.

\stopitemize

@@

\Frametitle {Performance Guarantee of DS}
\startitemize

@@

\stopitemize

@@

\Frametitle {Definition: Restricted Isometry Property}
\startitemize

@@

\Frametitle {Orthogonal Matching Pursuit}
\startitemize

@@

\Frametitle {Recent Literature on Compressive Channel Sensing}
\startitemize

@@

\Frametitle {Our Work}
\startitemize

@@

\Frametitle {Channel Model}
\startitemize

@@

\Frametitle {Precoder Setting}
\startitemize

@@

\Frametitle {Effective Channel}
\startitemize

@@

\Frametitle {Proposed Program}
\startitemize

@@

\Frametitle {Proof (1/3)}
\Disp{
D (\f')
:=&\left| \sum_{n=0}^{N_H-1} \RM{e}^{i n \f'} \right|
=\F{|\sin (N_H \f'/2)|}{|\sin (\f' /2)|} \\
\left| x -\F{x^3}{6} \right|
\leq &\sin x, \quad -\pi \leq x \leq \pi \\
\left| D (\f') \right|
= &\F{48}{|\f'^2 -24| |\f'|}
}
\startitemize[n]

@@

\Frametitle {Proof (2/3)}
\Disp{
\M{K}^\H \V{a}(\f) (k)
=&\F{1}{N_H} D \left( \f -\F{2 \pi k} {N_H} \right) \\
R(\eta)
:=&\F{1}{N_H} \sum_{n_H =s}^{N_H -1} D \left( \eta +\F{2 \pi n_H} {N_H} \right) \\
R(\eta) -\F{2\pi} {N_H}
\leq &\F{1}{N_H} N_H \int_{\f'=2\pi L/N_H}^{2\pi} |D(\f')| d \f'
}
\startitemize[n]

@@

\Frametitle {Proof (3/3)}
\Disp{
R(\f)
\leq &\F{1}{2\pi} \int_{\f'=2\pi L/N_H}^{2\pi} \F{48}{(24 -\f'^2) \f'} d \f'
+\F{2\pi} {N_H} \NT \\
=&\F{1}{\pi} \log \F{2\pi N_H}{L}
-\F{1}{N_H} \log \F{4\pi^2 -24} {L^2/N_H^2 -24}
+\F{2\pi} {N_H} \\
\leq &\F{1}{\pi} \log \F{N_H}{L}.
}
\startitemize[n]

@@

\Frametitle {Lemma: RIP Probability w.r.t.\ \m {}}
Let \m {} be i.i.d.\ Radmacher, as defined in Lemma ().
Then \m {} is RIP according to \m {} for at least probability
\Disp{
1 -2 \left( \F{12}{\d} \right)^s \exp \left[ - \left( \F{\epsilon^2}{4} -\F{\epsilon^3}{6} \right) \F{\d}{2} N_p \right]
}
{\small Source: Baraniuk, Davenport, DeVore, and Wakin (2008), ``A Simple Proof of the Restricted Isometry Property for Random Matrices''}

@@

\Frametitle {Preparation for the Proof}
\startitemize

\I Use \m {} in our case
\I Let \m {} be the index set of the largest \m {} components of \m {}, \m {} be the index set of the largest \m {} position of \m {} except \m {}, and \m {}
\I Denote as \m {} the columns of \m {} having indices in \m {}.
\I Denote \m {}

\stopitemize

\Frametitle {Lemmata on Vector Supports}
\startitemize

\I \m {}
\I \m {}
\startitemize

\I (modified to account nonzero \m {})

\stopitemize

\stopitemize
{\small Source: Cand\`es and Tao (2007), ``The Dantzig Selector''}

\Frametitle {Lemmata on RIP Matrix}
For overwhelming probability,
\startitemize

\I \m {}
\I \m {}
\startitemize

\I (generalized from real case)

\stopitemize
\I \m {}
\startitemize

\I (generalized from real case)

\stopitemize

\stopitemize
{\small Source: Cand\`es and Tao (2007), ``The Dantzig Selector''}

\Frametitle {Proof (1/4)}
\Disp{
\|\M{P}_{\MC{A}\MC{B}}^\Tr \M{P} \V{d}\|_2
\leq &\|\M{P}^\Tr \M{P} \V{d}\|_2 \NT \\
\leq &\R{N_g} \|\M{P}^\Tr \M{P} \V{d}\|_\infty \NT \\
\leq &4 \R{ N_g \log N_g }
}
\startitemize[n]

\I Inclusion of larger support
\I \m {} norm inequality
\I Plug in the Lemma for \m {}

\stopitemize

\Frametitle {Proof (2/4)}
\Disp{
\| \V{d}_{A} \|_1
\leq &\R{L} \| \V{d}_{A} \|_2 \NT \\
\leq &\R{L} \| \V{d}_{\MC{AB}} \|_2 \NT \\
\leq &\F {\d_{3L}} {1-\d_{2L}} \| \V{d}_{\MC{C}} \|_1 +\F {4} {1-\d_{2L}} \R{L N_g \log N_g} 
}
\startitemize[n]

\I \m {} norm inequality
\I Inclusion of larger support
\I Plug in the Lemma for \m {}

\stopitemize

\Frametitle {Proof (3/4)}
\Disp{
\| \V{d}_{\MC{C}} \|_1
\leq &\| \V{d}_{\MC{A}} \|_1 +2 \| \V{g}_{\MC{C}} \|_1 \NT \\
\leq &\F {\d_{3L}} {1-\d_{2L}} \| \V{d}_{\MC{C}} \|_1
+\F {4} {1-\d_{2L}} \R{L N_g \log N_g}
+2 \| \V{g}_{\MC{C}} \|_1 \\
\| \V{d}_{\MC{C}} \|_1
\leq &\F {4} {1-\d_{2L} -\d_{3L}} \R{L N_g \log N_g}
+2 \F{1-\d_{2L}} {1 -\d_{2L} -\d_{3L}} \| \V{g}_{\MC{C}} \|_1
}
\startitemize[n]

\I Copy the Lemma for \m {}
\I Plug in the previous eqn.\ for \m {}
\I Cancellation, simplification

\stopitemize

\Frametitle {Proof (4/4)}
\Disp{
\| \V{d} \|_2^2
\leq &\|\V{d}_{\MC{A}\MC{B}}\|_2^2 +\F{1}{L} \|\V{d}_{\MC{C}}\|_1^2 \NT \\
\leq & \left( \F{\d_{3L}^2} {L^2 (1-\d_{2L})^2} +\F{1}{L} \right) \|\V{d}_{\MC{C}}\|_1^2 \NT \\
&\quad +\F{8 \d_{3L}} {L (1-\d_{2L})^2} \R{N_g \log N_g} \|\V{d}_{\MC{C}}\|_1 \NT \\
&\quad +\F{16}{(1-\d_{2L})^2} N_g \log N_g \\
\|\V{d}\|_2^2
\leq &\F{1}{4 \pi^4} \d_{3L}^4 (1-2\d_{2L}) L^4 ( \log N_g )^4
}
\startitemize[n]

\I Copy the Lemma for \m {}
\I Plug in the Lemma for \m {}
\I Plug in the Lemma for \m {}, approximate using \m {}, and \m {}

\stopitemize

\Frametitle {Conclusion}
\startitemize[n]

\I We are concerned with effective and estimation of MIMO mm-wave channel by exploiting its sparsity
\I We adopt The Dantzig Selector (DS) rather than Orthogonal Matching Pursuit (OMP), like many of past literature, as the estimation algorithm
\I We generalized DS for complex vectors, and we carried it out in the spatial frequency domain \m {}
\I Analogous to original DS proof, we proved explicitly that the probability that the expected square error is bounded is overwhelming, where the bounding constant is an explicit function of \m {}, the number of path

\stopitemize

\Frametitle {Future Work}
It remains to
\startitemize[n]

\I Find the explicit ``overwhelming'' probability
\I Transform DS into Second Order Cone Problem
\I Find the Lagrangian and dual problem
\I Write the simulation, using Newton method
\I Compare the probability bound with the simulation result

\stopitemize

\Frametitle {References}
\startitemize[n]

{ \small
\I W U Bajwa, J Haupt, G Raz, and R Nowak (2008), ``Compressed Channel Sensing'', 2008 42nd Annual Conference on Information Sciences and Systems.
\I R Baraniuk, M Davenport, R DeVore, and M Wakin (2008), ``A Simple Proof of the Restricted Isometry Property for Random Matrices'', \textit{Constructive Approximation} \textbf{28}: 253–263
\I S Boyd, L Vandenberghe (2004), \textit{Convex Optimization}. Cambridge U.\ Press.
\I E J Cand\`es and J Romberg (2005), ``\m {}-MAGIC: Recovery of Sparse Signals via Convex Programming'', Retrieved from \url{https://statweb.stanford.edu/~candes/l1magic/downloads/l1magic.pdf}.
}
\setcounter{countRef}{\value{enumi}}

\stopitemize

\Frametitle {References}
\startitemize[n]

\setcounter{enumi}{\value{countRef}} { \small
\I E J Cand\`es and T Tao (2005), ``Decoding by Linear Programming'', \textit{IEEE Transactions on Information Theory}, Vol.51, No.12.
\I E Cand\`es and T Tao (2007), ``The Dantzig Selector: Statistical Estimation when \m {} is Much Larger than \m {}'', \textit{The Annals of Statistics}, Vol.35, No.6.
\I J A Tropp and A C Gilbert (2007a), ``Signal Recovery from Random Measurements via Orthogonal Matching Pursuit: The Gaussian Case'', Caltech, ACM Tech.\ Rep. Retrieved from: \url{www.acm.caltech.edu/~jtropp/reports/TG07-Signal-RecoveryTR.pdf}
\I J A Tropp and A C Gilbert (2007b), ``Signal Recovery From Random Measurements via Orthogonal Matching Pursuit'', \textit{IEEE Transactions on Information Theory}, Vol.\ 53, No.\ 12.
}

\stopitemize

>>>>

\input {./1_slide.tex}
\input {./2_slide.tex}
\input {./3_slide.tex}
\input {./4_slide.tex}
\input {./5_slide.tex}

@@

@@

\Frametitle {Performance Guarantee of DS}

@@

@@

\Frametitle {Definition: Restricted Isometry Property}

@@

\Frametitle {Orthogonal Matching Pursuit}

@@

\Frametitle {Recent Literature on Compressive Channel Sensing}

@@

\Frametitle {Our Work}

@@

\Frametitle {Channel Model}

@@

\Frametitle {Precoder Setting}

@@

\Frametitle {Effective Channel}

@@

\Frametitle {Proposed Program}

@@

\Frametitle {Proof (1/3)}
\Disp{
D (\f')
:=&\left| \sum_{n=0}^{N_H-1} \RM{e}^{i n \f'} \right|
=\F{|\sin (N_H \f'/2)|}{|\sin (\f' /2)|} \\
\left| x -\F{x^3}{6} \right|
\leq &\sin x, \quad -\pi \leq x \leq \pi \\
\left| D (\f') \right|
= &\F{48}{|\f'^2 -24| |\f'|}
}

@@

\Frametitle {Proof (2/3)}
\Disp{
\M{K}^\H \V{a}(\f) (k)
=&\F{1}{N_H} D \left( \f -\F{2 \pi k} {N_H} \right) \\
R(\eta)
:=&\F{1}{N_H} \sum_{n_H =s}^{N_H -1} D \left( \eta +\F{2 \pi n_H} {N_H} \right) \\
R(\eta) -\F{2\pi} {N_H}
\leq &\F{1}{N_H} N_H \int_{\f'=2\pi L/N_H}^{2\pi} |D(\f')| d \f'
}

@@

\Frametitle {Proof (3/3)}
\Disp{
R(\f)
\leq &\F{1}{2\pi} \int_{\f'=2\pi L/N_H}^{2\pi} \F{48}{(24 -\f'^2) \f'} d \f'
+\F{2\pi} {N_H} \NT \\
=&\F{1}{\pi} \log \F{2\pi N_H}{L}
-\F{1}{N_H} \log \F{4\pi^2 -24} {L^2/N_H^2 -24}
+\F{2\pi} {N_H} \\
\leq &\F{1}{\pi} \log \F{N_H}{L}.
}

@@

@@

### 2019-08-31 presentation/1_introduction.tex
Code: Change plot marker

\I Problem Setting and Proposed Method

\I Proving the performance bound: Sparsity, Concentration Inequality, and Expected Error

\I Conclusion and Future Work

\I References
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Background}
{
\I Multiple-input-multiple-output (MIMO) wireless communication is expected to be the next-generation r\'egime.

@@

\I Meanwhile, millimeter wave (mmWave) channels often exhibit sparse properties.

\I Under mmWave setting, if the sparsity is exploited, can few observations suffice to estimate the channel?
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Compressive Sensing}
{
\I The situation that the number of model parameters is much larger than the number of measurements has been well studied, and and \Emph {compressed sensing} (CS) address exactly that.

>>>>

\I Problem setting and proposed method

\I Proving the performance bound: sparsity, concentration inequality, and expected error

\I Simulation (preliminary)

\I Conclusion and future work

\I References
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Background}
{
\I \Emph {Multiple-input-multiple-output} (MIMO) wireless communication is expected to be the next-generation r\'egime.

@@

\I Meanwhile, \Emph {millimeter wave} (mmWave) channels often exhibit sparse properties.

\I Under mmWave setting, if the \Emph {sparsity} is exploited, it turns out few observations may suffice to estimate the channel.
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Compressive Sensing}
{
\I The situation that the number of model parameters is much larger than the number of measurements has been well studied, and and \Emph {compressed sensing} (CS) address exactly that.

### 2019-08-31 report/2_problem_setting.tex
Code: Change plot marker

We restrict our consideration to the uniform linear array, which can be modeled as
\Disp {
\NC \V {a} \SB {\psi'}
\in \NC \MB {V}_\MB {C} \SB {N_H} \NR
\NC \V {a} \SB {\psi'}
= \NC \F {1}{\R {N_H}} \sum_{n=0}^{N-1} \Ss {e}^{n \psi' \Ss {i}} \V {u}_n \NR
}
where \m {\Ss {e}} is the base of natural logarithm, and \m {\Ss {i}} the imaginary unit.

And consider the virtual representation of the MIMO channel (see for example Akdeniz et.\ al.\ 2014).
\Disp {
\NC \M{H}
=\NC \sum_{l=0} ^{L-1}
\a_l
\V {a} \SB { \F {d_{\Rm {arr}}} {\l _{\Rm {arr}} \sin \f_l' }}
\V {a} \SB { \F {d_{\Rm {arr}}} {\l _{\Rm {arr}} \sin \th_l' }}^\Adj \NR[+]
}
The physical meaning of \m {\th_l} is the \m {l}-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \m {\th_l}, the \m {l}-th that of arrival wave, while \m {d_{\Rm {arr}}} is the distance between two adjacent antennae.
For our purpose, we may absorb the argument of \m {\V {a}} as
\Disp {
\NC \f_l
= \NC \RB {
\F {d_{\Rm {arr}}} {\l_{\Rm {arr}}} \sin \f_l'
\; \Rm{Mod}\; \RB {2\pi}
} \NR[+]
\NC \th_l
= \NC \RB {
\F {d_{\Rm {arr}}} {\l_{\Rm {arr}}} \sin \th_l'
\; \Rm{Mod}\; \RB {2\pi}
} \NR[+]
}
to get a simpler form
\Disp {
\NC \M{H}
\in \NC \MB {M}_\MB {C} \SB {N_H} \NR
\NC \M{H}
=\NC \sum_{l=0} ^{L-1} \a_l \V {a} \SB {\f_l} \V {a} \SB {\th_l}^\Adj \NR
}

>>>>

We restrict our consideration to the uniform linear array, which can be modeled as
\Disp {
\NC \V {a} \SB {\psi'}
\in \NC \MB {V}_\MB {C} \SB {N_H} \NR
\NC \V {a} \SB {\psi'}
= \NC \F {1}{\R {N_H}} \sum_{n_h=0}^{N_H-1} \Ss {e} ^{\Ss {i} n_h \psi'} \V {u}_{n_h} \NR
}
where \m {\Ss {e}} is the base of natural logarithm, and \m {\Ss {i}} the imaginary unit.

And consider the virtual representation of the MIMO channel (see for example Akdeniz et.\ al.\ 2014).
\Disp {
\NC \M{H}
=\NC \sum_{l=0} ^{L-1}
\a_l
\V {a} \SB { 2\pi \F {d_{\Rm {arr}}} {\l _{\Rm {arr}}} \sin \f_l'}
\V {a} \SB { 2\pi \F {d_{\Rm {arr}}} {\l _{\Rm {arr}}} \sin \th_l'}^\Adj \NR[+]
}
The physical meaning of \m {\th_l} is the \m {l}-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \m {\th_l}, the \m {l}-th that of arrival wave, while \m {d_{\Rm {arr}}} is the distance between two adjacent antennae.
For our purpose, we may absorb the argument of \m {\V {a}} as
\Disp {
\NC \f_l
= \NC \RB {
  2\pi \F {d_{\Rm {arr}}} {\l_{\Rm {arr}}} \sin \f_l'
  \; \Rm{Mod}\; \RB {2\pi}
} \NR[+]
\NC \th_l
= \NC \RB {
  2\pi \F {d_{\Rm {arr}}} {\l_{\Rm {arr}}} \sin \th_l'
  \; \Rm{Mod}\; \RB {2\pi}
} \NR[+]
}
to get a simpler form
\Disp {
\NC \M{H}
\in \NC \MB {M}_\MB {C} \SB {N_H} \NR
\NC \M{H}
=\NC \sum_{l=0} ^{L-1} \a_l \V {a} \SB {\f_l} \V {a} \SB {\th_l}^\Adj \NR
}
